|

### 2022-02-14 README.Rmd
lit and tables

### ICBe preparation
  - Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates `/replication_paper/data/in/icb_manual_recording_master_sheet.xlsx`
  - Lit review and tree/leaf codebook: `/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx`
  - Case study tables: `/replication_paper/data/in/CaseStudies.xlsx`

>>>>

### ICBe preparation
  - Cleaning dictionaries: used to clean raw codings for actors, actions, locations, and dates `/replication_paper/data/in/icb_manual_recording_master_sheet.xlsx`
  - Lit review and tree/leaf codebook: `replication_data/in/icbe_litreview_trees_sentences.xlsx` and `/replication_paper/data/in/icbe_litreview_trees_sentences.xlsx`
  - Case study tables: `/replication_paper/data/in/CaseStudies.xlsx`

### 2022-02-14 replication_paper/IntroducingICBe_DouglassEtAl_2021_BetaDraft_bookdown.Rmd
lit and tables

Successful measurement requires the existence of an unobserved latent state among all possible states, $\omega \in \Omega$ and a systematic data generating process (DGP) that converts that state into observables that enter the historical record, $X=f(\omega)$. We organize our prior beliefs about possible states, $\Omega$, and the DGP, $f()$, along two overarching axes, summarized in detail by Table \ref{tbl:litreview}. The first axes (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology. We employ a metaphor of international affairs as a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do). Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict). The resulting codebook for events includes 117 different verbs and is available in full in the online material.^[See the Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]

@@

```{r, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F,  ft.arraystretch=0.75}

@@

litreview_ft %>%
  flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
  flextable_to_rmd()
```

@@

Going further, we examine accepted tokens side-by-side with the original source material. We perform stratified sampling across the semantic space, and provide comparisons for 15 sentences here in Table \ref{tbl:15samplesentences}, 50 more in the online Appendix \ref{app:50samplesentences}, and the full set online. To enhance readability, we map selected tokens into a form sentence more akin to the source sentence (original tokens shown underlined). At the sentence level, we find codings accurately reflect the key events of the text. Further, we note that human-in-the-loop coding correctly performs entity resolution, which is often not explicitly mentioned in the text, posing a problem for automated systems.

@@

codings_wide_agreed_embeded_stratified_sample_ft_smaller <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft_smaller.Rds')) %>%
  flextable::set_caption("ICBe Codings for a Stratified Sample of Sentences (15) \\label{tbl:15samplesentences}") 
codings_wide_agreed_embeded_stratified_sample_ft_smaller

@@

Recall of critical events for ICBe and other state-of-the-art systems are shown in Table \ref{tbl:casestudy196}. ICBe records 8 of 10 critical events identified by the case history. It misses the mobilization of Cuba's military forces, owing to an emphasis of the ICB crisis narrative on the United States and the Soviet Union as the primary actors. It also misses the secondary events of the inconveniently timed nuclear weapons tests by both the United States and the Soviet Union, which was also excluded from the narrative.

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
CaseStudy196_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy196_ft.Rds'))
CaseStudy196_ft %>%
  flextable::set_caption("Cuban Missile Crisis ground truth and event data \\label{tbl:casestudy196}") %>%
    flextable::width( j = 1, width=0.5)  %>%
    flextable::width( j = 2, width=1.25)  %>%
    flextable::width( j = 3, width=0.5) %>%
    flextable::width( j = 4, width=1.1) %>%
    flextable::width( j = 5, width=1) %>%
    flextable::width( j = 6, width=0.75) %>%
    flextable::width( j = 7, width=0.65)

@@

Recall of critical events is shown in Table \ref{tbl:casestudy426} below. ICBe records 10 of 14 critical events identified by the case history. It performs poorly on subnational conflict events, missing the formation of the RCD, the deployment of a U.N. peacekeeping mission, the withdraw of Rwandan troops following the peace agreements, and the separate peace struck with the rebel groups RDC and MLC. These details were under-textualized in the ICB narrative. Temporal coverage of this more recent crisis was much greater across datasets, and so we can compare the ICBe codings to five other event-level and two episode-level datasets. As before, Cameo dictionary codings from the Cline Center's historical Phoenix dataset offer possible coverage of 8 events. Cameo codings from Terrier, which includes a much larger number of news sources from the LexisNexis database, only provide possible coverage of one event. The DARPA-funded ICEWs system produces possible coverage of 7 events and notably was the only system to catch the assassination of Kabila. The MIDs incident-level dataset includes possible coverage of 4 events. MIDs episode-level data incorporates possible coverage of 6 events. Finally, Dyadic ICB data cover 7 events.

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
CaseStudy426_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy426_ft.Rds'))
CaseStudy426_ft  %>%
  flextable::set_caption("DRC Civil War ground truth and event data \\label{tbl:casestudy426}") %>%
      width(j=1, width=0.5) %>%
      width(j=2, width=0.75) %>%
      width(j=3, width=0.3) %>%
      width(j=4, width=0.65) %>%
      width(j=5, width=1.0) %>%
      width(j=6, width=0.5) %>%
      width(j=7, width=0.75) %>%
      width(j=8, width=0.75) %>%
      width(j=9, width=0.5) %>%
      width(j=10, width=0.5)

@@

# Online Appendix

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
codings_wide_agreed_embeded_stratified_sample_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds')) %>%
  flextable::set_caption("ICBe Codings for 50 Sample Sentences \\label{tbl:50samplesentences}")

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
ft_sentence_table_196 <- readRDS(file=paste0(here::here(), '/replication_paper/tables/sentence_tables/ft_sentence_table_196.Rds'))  %>%
  flextable::set_caption("ICBe Codings for Cuban Missile Crisis (Crisis 196) \\label{tbl:ft_sentence_table_196}") 
ft_sentence_table_196 %>%
      flextable::width( j = 1, width=0.3) %>%
      flextable::width( j = 2, width=3.25) %>%
      flextable::width( j = 3, width=3.25)
```

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
ft_sentence_table_426 <- readRDS(file=paste0(here::here(), '/replication_paper/tables/sentence_tables/ft_sentence_table_426.Rds'))  %>%
  flextable::set_caption("ICBe Codings for DRC Civil War (Crisis 426) \\label{tbl:ft_sentence_table_426}") 
ft_sentence_table_426 %>%
      flextable::width( j = 1, width=0.3) %>%
      flextable::width( j = 2, width=3.25) %>%
      flextable::width( j = 3, width=3.25)
```

>>>>

Successful measurement requires the existence of an unobserved latent state among all possible states, $\omega \in \Omega$ and a systematic data generating process (DGP) that converts that state into observables that enter the historical record, $X=f(\omega)$. We organize our prior beliefs about possible states, $\Omega$, and the DGP, $f()$, along two overarching axes, summarized in detail by Table 1. <!-- {tbl:litreview}  -->The first axes (rows) represents the types of information we expect to find in IR and forms the basis for our proposed ontology. We employ a metaphor of international affairs as a chess game, with players (polities, rebel groups, IGOs, etc.), pieces (military platforms, civilians, domains), and behaviors (think, say, do). Precise sequencing is required to capture gambits (sequences of moves) and outcomes (victory, defeat, peace, etc.), while precise geo-coding is required to understand the chessboard (medium of conflict). The resulting codebook for events includes 117 different verbs and is available in full in the online material.^[See the Github Repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$).]

@@

```{r litreview, eval=T, echo=F, results='asis', include=T, message=F, cache=F, warning=F, ft.arraystretch=0.75}

@@

litreview_ft %>%
  flextable::set_caption(caption = "Prior Beliefs, State of the Art, and Existing Data") %>%
  # flextable::set_caption("Prior Beliefs, State of the Art, and Existing Data \\label{tbl:litreview}")  %>% 
  flextable_to_rmd()
```

@@

Going further, we examine accepted tokens side-by-side with the original source material. We perform stratified sampling across the semantic space, and provide comparisons for 15 sentences here in Table 2,<!-- \ref{tbl:15samplesentences} --> 50 more in the Appendix \ref{app:50samplesentences}, and the full set online. To enhance readability, we map selected tokens into a form sentence more akin to the source sentence (original tokens shown underlined). At the sentence level, we find codings accurately reflect the key events of the text. Further, we note that human-in-the-loop coding correctly performs entity resolution, which is often not explicitly mentioned in the text, posing a problem for automated systems.

@@

codings_wide_agreed_embeded_stratified_sample_ft_smaller <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft_smaller.Rds')) %>%
  flextable::set_caption("ICBe Codings for a Stratified Sample of Sentences (15)") 
codings_wide_agreed_embeded_stratified_sample_ft_smaller

@@

Recall of critical events for ICBe and other state-of-the-art systems are shown in Table 3.<!-- \ref{tbl:casestudy196} --> ICBe records 8 of 10 critical events identified by the case history. It misses the mobilization of Cuba's military forces, owing to an emphasis of the ICB crisis narrative on the United States and the Soviet Union as the primary actors. It also misses the secondary events of the inconveniently timed nuclear weapons tests by both the United States and the Soviet Union, which was also excluded from the narrative.

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
CaseStudy196_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy196_ft.Rds'))
CaseStudy196_ft %>%
  flextable::set_caption("Cuban Missile Crisis ground truth and event data") %>%
    flextable::width( j = 1, width=0.5)  %>%
    flextable::width( j = 2, width=1.25)  %>%
    flextable::width( j = 3, width=0.5) %>%
    flextable::width( j = 4, width=1.1) %>%
    flextable::width( j = 5, width=1) %>%
    flextable::width( j = 6, width=0.75) %>%
    flextable::width( j = 7, width=0.65)

@@

Recall of critical events is shown in Table 4 below.<!-- \ref{tbl:casestudy426} --> ICBe records 10 of 14 critical events identified by the case history. It performs poorly on subnational conflict events, missing the formation of the RCD, the deployment of a U.N. peacekeeping mission, the withdraw of Rwandan troops following the peace agreements, and the separate peace struck with the rebel groups RDC and MLC. These details were under-textualized in the ICB narrative. Temporal coverage of this more recent crisis was much greater across datasets, and so we can compare the ICBe codings to five other event-level and two episode-level datasets. As before, Cameo dictionary codings from the Cline Center's historical Phoenix dataset offer possible coverage of 8 events. Cameo codings from Terrier, which includes a much larger number of news sources from the LexisNexis database, only provide possible coverage of one event. The DARPA-funded ICEWs system produces possible coverage of 7 events and notably was the only system to catch the assassination of Kabila. The MIDs incident-level dataset includes possible coverage of 4 events. MIDs episode-level data incorporates possible coverage of 6 events. Finally, Dyadic ICB data cover 7 events.

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
CaseStudy426_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/CaseStudy426_ft.Rds'))
CaseStudy426_ft  %>%
  flextable::set_caption("DRC Civil War ground truth and event data") %>%
      width(j=1, width=0.5) %>%
      width(j=2, width=0.75) %>%
      width(j=3, width=0.3) %>%
      width(j=4, width=0.65) %>%
      width(j=5, width=1.0) %>%
      width(j=6, width=0.5) %>%
      width(j=7, width=0.75) %>%
      width(j=8, width=0.75) %>%
      width(j=9, width=0.5) %>%
      width(j=10, width=0.5)

@@

# Appendix

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
codings_wide_agreed_embeded_stratified_sample_ft <- readRDS(file=paste0(here::here(), '/replication_paper/tables/codings_wide_agreed_embeded_stratified_sample_ft.Rds')) %>%
  flextable::set_caption("ICBe Codings for 50 Sample Sentences") # \\label{tbl:50samplesentences}

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
ft_sentence_table_196 <- readRDS(file=paste0(here::here(), '/replication_paper/tables/sentence_tables/ft_sentence_table_196.Rds'))  %>%
  flextable::set_caption("ICBe Codings for Cuban Missile Crisis (Crisis 196)") # \\label{tbl:ft_sentence_table_196}
ft_sentence_table_196 %>%
      flextable::width( j = 1, width=0.3) %>%
      flextable::width( j = 2, width=3.25) %>%
      flextable::width( j = 3, width=3.25)
```

@@

```{r, eval=T, echo=F, results='markup', include=T, message=F, cache=F, warning=F,  ft.arraystretch=1}
ft_sentence_table_426 <- readRDS(file=paste0(here::here(), '/replication_paper/tables/sentence_tables/ft_sentence_table_426.Rds'))  %>%
  flextable::set_caption("ICBe Codings for DRC Civil War (Crisis 426)") #\\label{tbl:ft_sentence_table_426}
ft_sentence_table_426 %>%
      flextable::width( j = 1, width=0.3) %>%
      flextable::width( j = 2, width=3.25) %>%
      flextable::width( j = 3, width=3.25)
```
